Democracy, Public Support, and Measurement Uncertainty

### 2021-04-27 paper/dcpo_demsupport.Rmd
issues in num of country name at 434

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    arrange(country, year)
  return(df_temp)
}
```

@@

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    left_join(sd_control, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

>>>>

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    dplyr::arrange(country, year)
  return(df_temp)
}
```

@@

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    dplyr::left_join(sd_control, by = c("country", "year")) %>% 
    dplyr::mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})
